SoK: Transparent Dishonesty. Front-running attacks on Blockchain.

### 2018-12-07 frontrunning/Latex/sections/paper.tex
tod written

We classify the mitigations into three main categories. In the first category, the blockchain removes the miner's ability to arbitrarily order transactions and tries to enforce some ordering, or queue, for the transactions. In the second category, cryptographic techniques are used to limit the visibility of transactions, giving the potential front-running less information to base their strategy on. In the final category, dapps are designed from the bottom-up to remove the importance of transaction ordering or time in their operations.

We also note that for dapps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent. We do not discuss this further here; see Appendix ~\ref{app:traditionalprevention}.

%\subsection{Front-Running Resistant Blockchains}
\subsection{Transaction Queue}

% Jeremy: to do

Transaction chaining -> resolve conflicts -> topological order/sort (also consider total order) -> cf UTXOs

FIFO -> consensus on FI -> possible in theory
-> could be solved with TTP -> censorship still possible (completeness issue)

FI_O -> FIRO -> deterministic random order -> manipulatable (malleability in the collection and your own items in the collection and maybe and other items in the collection) -> CTOR

@@

An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction hash~\cite{bitcoinABC2018CTOR}. This solution can potentially mitigate the re-ordering attack by miners, however it does not prevent it fully. 
%NOTE: the two solutions above are both on the transaction ordering, however Silva's solution requires a logical timestamp, and CTOR uses sorting based on transaction hash.

>>>>

We classify the mitigations into three main categories. In the first category, the blockchain removes the miner's ability to arbitrarily order transactions and tries to enforce some ordering, or queue, for the transactions. In the second category, cryptographic techniques are used to limit the visibility of transactions, giving the potential front-running less information to base their strategy on. In the final category, dapps are designed from the bottom-up to remove the importance of transaction ordering or time in their operations. We also note that for dapps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent. We do not discuss this further here; see Appendix ~\ref{app:traditionalprevention}.

%\subsection{Front-Running Resistant Blockchains}
\subsection{Collection Sequencing}

Miners on Ethereum store pending transactions in a pool and draw from them when forming a block. As the term `pool' implies, there is no instinct order to how transactions are drawn from the pool and miners are free to sequence them arbitrarily.\footnote{Sometimes the pool is called a `queue.' It is important to note is a misnomer as queues use a first-in-first-out sequence.} This enables certain kinds of front-running, in particular transactions the miner will place before a pending transaction. A number of proposals attempt to thwart this attack by enforcing a rule about how to sequence transactions.

First-in-first-out (FIFO) is generally not possible on a distributed network because transactions can reach different nodes in a different order. While the network could form a consensus based on locally observed FIFO, but this would increase the rate of orphaned blocks, as well as adding complexity to the protocol. A trusted third party could be used to assign sequential numbers to transactions (and sign them), but this is contrary to the blockchain's core innovation of distributed trust.

An alternative is to sequence transactions psuedorandomly. This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) in Bitcoin cash which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}. Note that Bitcoin cash does not have a front-running problem for most standard transactions. While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks. A front-runner can construct multiple equivalent transactions, with slightly different values, until she finds a candidate that positions her transaction a desirable location in the resulting sequence. She broadcasts only this transaction and now miners that include her transaction will position in front of transactions they heard about much earlier.

Finally, transactions themselves could enforce order. In particular, they could point to the current state of the contract and only execute on that exact state. This transaction chaining only prevents certain sub-types of front-running. For example, it could prevent scalping attacks: if Alice buys from a marketplace that matches her order to Bob with a price improvement, a miner could buy from Bob first and then execute Alice's original transaction which results in her being matched to Alice instead. Alternatively, if Alice registers an interesting-looking domain name, transaction chaining does not stop a miner from replacing Alice's request with her own. Transaction chaining would likely lead to more orphaned transactions for active contracts, as only one state-changing transaction would be allowed per state.

@@

%An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction hash~\cite{bitcoinABC2018CTOR}. This solution can potentially mitigate the re-ordering attack by miners, however it does not prevent it fully. 
%NOTE: the two solutions above are both on the transaction ordering, however Silva's solution requires a logical timestamp, and CTOR uses sorting based on transaction hash.
